---
title: "ILXSM Update"
author: "Sarah Salois, Thomas Swiader"
date: "7/12/2024"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_fold: hide
    number_sections: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```


```{r, data}
# testing
library(dplyr)
library(ggplot2)
library(sf)
library(patchwork)
library(ecodata)
lw_data <- read.csv(here::here('data/ilxsm/ILXSM_EntirePull_10-09-2024.csv'))

# Coastal shapefiles
load(here::here('shapefiles/nes_map.Rdata'))

# canada <- sf::st_read(here::here('shapefiles/Canada.shp'), quiet = TRUE) %>%
#   sf::st_set_crs(4326) 
# usa <- sf::st_read(here::here('shapefiles/USA.shp'), quiet = TRUE) %>%
#   sf::st_set_crs(4326) 
# sf::sf_use_s2(FALSE)
# us.coast = sf::st_union(usa %>% sf::st_as_sf())
# ca.coast = sf::st_union(canada %>% sf::st_as_sf())
```


```{r, wrangle}
# Make sure all data are in same units, if not convert
# just a check
# unique(lw_data$UNIT_MEASURE)
# "CM" "GM" "MM" "LB"
lbs <- which(lw_data$UNIT_MEASURE == 'LB')
# one rouge tally w/lbs but no param_value_num, so removing
chkme <- lw_data[lbs,]
# lw_data <- lw_data[-lbs,]
# one rouge tally w/lbs this one does have a param_value_num, fixing the unit
lw_data[row.names(chkme),"UNIT_MEASURE"] <- 'GM'
WT <- which(lw_data$PARAM_TYPE == 'WT') # None, so no need to adjust as below
lw_data <- lw_data %>%
  mutate(PARAM_VALUE_NUM = case_when(PARAM_TYPE == 'ML' & UNIT_MEASURE == 'CM' ~ PARAM_VALUE_NUM * 10, 
                            PARAM_TYPE == 'ML' & UNIT_MEASURE == 'MM'~ PARAM_VALUE_NUM, 
                           # PARAM_TYPE == 'WT' & UNIT_MEASURE == 'GM' ~ PARAM_VALUE_NUM,
                             PARAM_TYPE == 'OW' & UNIT_MEASURE == 'GM' ~ PARAM_VALUE_NUM))
cm <- which(lw_data$UNIT_MEASURE == 'CM')
#chkme2 <- lw_data[cm,]
lw_data[cm,"UNIT_MEASURE"] <- 'MM'
#unique(lw_data$UNIT_MEASURE)

lw_data$LAND_DATE <-lubridate::dmy(lw_data$LAND_DATE)
lw_data <- lw_data %>%
  mutate(year = lubridate::year(LAND_DATE),
         month = lubridate::month(LAND_DATE),
         week = lubridate::week(LAND_DATE), 
         day = lubridate::day(LAND_DATE))

unique_areas <- sort(unique(lw_data$AREA_CODE))

wt <- lw_data %>%
  filter(PARAM_TYPE =='OW') %>% 
  rename(weight = PARAM_VALUE_NUM)
ml <- lw_data %>%
  filter(PARAM_TYPE == 'ML') %>%
  rename(length = PARAM_VALUE_NUM)

ml.c <- ml %>% select(LAND_DATE,AREA_CODE,ORGANISM_ID, 
                                length,VESSEL_NAME, VTR_SERIAL_NUM)

wt.c <- wt %>% select(LAND_DATE,AREA_CODE,ORGANISM_ID, 
                                weight,VESSEL_NAME, VTR_SERIAL_NUM)

lw_paired <- right_join(ml.c, wt.c, 
                        by = c('LAND_DATE','AREA_CODE','ORGANISM_ID', 
                               'VESSEL_NAME', 'VTR_SERIAL_NUM'))

lw_paired <- na.omit(lw_paired)
lw_paired <- lw_paired %>% relocate(weight, .after = length)

lw_paired <- lw_paired %>%
  mutate(year = lubridate::year(LAND_DATE),
         month = lubridate::month(LAND_DATE),
         week = lubridate::week(LAND_DATE), 
         day = lubridate::day(LAND_DATE))



```




```{r, tally}
## Stat areas
stat.areas <- sf::st_read(here::here('shapefiles/groundfish_stat_areas.shp'),
                          quiet = TRUE) %>%
  sf::st_set_crs(4326) 

# Isolate stat areas fished from data frame
unq.stat.areas <- sort(unique(lw_data$AREA_CODE))
ilxsm.stat.areas <- stat.areas[na.omit(stat.areas$Id %in% unq.stat.areas),]

# For multiple polygons - use this!
stat.ctrds <- sf::st_point_on_surface(ilxsm.stat.areas)
# ggplot() +
#   geom_sf(data = ilxsm.stat.areas) +
#   geom_sf(data = stat.ctrds, color = "red", size = 0.1) +
#   theme_void()

# create a dataframe and isolate coordinates 
stat.areas.df <- stat.ctrds %>%
  dplyr::mutate(lon = sf::st_coordinates(.)[,1],
                lat = sf::st_coordinates(.)[,2]) %>% 
  as.data.frame()
un.df.sa = unique(stat.areas.df$Id)
# extract coordinates and save to squibs data
lw_data$stat.lat <- NA
lw_data$stat.lon <- NA
for (i in 1:length(un.df.sa)){
  tmp <- subset(lw_data, AREA_CODE == un.df.sa[i])
  locs <- which(lw_data$AREA_CODE %in% tmp$AREA_CODE)
  b <- subset(stat.areas.df, Id == un.df.sa[i], select = 'lat')
  c <- subset(stat.areas.df, Id == un.df.sa[i], select = 'lon')
  lw_data[locs,'stat.lat'] <- b$lat
  lw_data[locs,'stat.lon'] <- c$lon
}

# tally by stat area
df_tally_stat <- lw_data %>% 
  group_by(AREA_CODE, year) %>%
  summarise(n = length(ORGANISM_ID), 
            lon = mean(stat.lon), 
            lat = mean(stat.lat))


```

### ILXSM Spatial Extent

Map of Northeast United States Continental Shelf Large Marine Ecosystem (NES LME).
Bathymetry is indicated by a dark grey contours. The black polygons overlaid on 
the bathymetry depict the boundaries of the [Greater Atlantic Region Fisheries 
Statistical Areas](https://www.fisheries.noaa.gov/resource/map/greater-atlantic-region-statistical-areas). The location of each circle demarks the centroid of the statistical area
polygon. Note that each circle is located at the center coordinates of the 
statistical area and does not represent specific fishing coordinates to ensure 
confidentiality. The color of the circle indicates the collection year, where 
yellow = 2021, purple = 2022, magenta = 2023, and peach = 2024. The size of 
each point represents the number of northern shortfin squid 
(*Illex illecebrosus*) samples reported through Shortfin Squid Electronic Size 
Monitoring Pilot Project in the associated statistical area. 

```{r, maps}

# bathy <- marmap::getNOAA.bathy(-80,-58, 33, 46)
# bathy = marmap::fortify.bathy(bathy)
#2021
ggplot() +
 geom_sf(data = us.coast %>% st_as_sf(), color = 'gray20', fill = 'lightgrey') +
  geom_sf(data = ca.coast %>% st_as_sf(), color = 'gray20', fill = 'lightgrey') +
  geom_sf(data = ilxsm.stat.areas %>% st_as_sf() ,  
          fill = NA, color = 'gray20', lwd = 0.6) +
  geom_contour(data = bathy,
               aes(x=x,y=y,z=-1*z),
               breaks=c(0,50,100,200, Inf),
               linewidth=c(0.3),
               col = 'darkgrey') +
  geom_point(data = df_tally_stat %>% filter(year == 2021),
             aes(x = lon, y = lat, size = n), 
             color = 'black', bg = 'gold1',
             pch = 21) +
  labs(size = 'No. of Squid') + 
  geom_text()+
  annotate('text', label = '2021', x = -74.5, y = 43.5, size = 8, 
           colour = 'black' ) +
  coord_sf(xlim = c(-76,-66.0), ylim = c(35.5,44), datum = sf::st_crs(4326)) +
  xlab('Longitude') + 
  ylab('Latitude') +
  theme_bw() + 
  theme(legend.position = c(0.85, 0.2)) +
  theme(legend.background = element_rect(linetype="solid", 
                                         colour ="grey20")) +
  theme(legend.key.size = unit(0.5, 'cm')) + 
  theme(axis.text = element_text(size = 13), 
        axis.title = element_text(size = 15),
        axis.ticks.length = unit(-1.4, "mm")) 
# save
ggsave(path = here::here('figures'),'ilxsm_2021.png',
       width = 10, height = 8, units = "in", dpi = 300)
#2022
ggplot() +
 geom_sf(data = us.coast %>% st_as_sf(), color = 'gray20', fill = 'lightgrey') +
  geom_sf(data = ca.coast %>% st_as_sf(), color = 'gray20', fill = 'lightgrey') +
  geom_sf(data = ilxsm.stat.areas %>% st_as_sf() ,  
          fill = NA, color = 'gray20', lwd = 0.6) +
  geom_contour(data = bathy,
               aes(x=x,y=y,z=-1*z),
               breaks=c(0,50,100,200, Inf),
               linewidth=c(0.3),
               col = 'darkgrey') +
  geom_point(data = df_tally_stat %>% filter(year == 2022),
             aes(x = lon, y = lat, size = n), 
             color = 'black', bg = 'slateblue3',
             pch = 21) +
  labs(size = 'No. of Squid') +
  geom_text()+
  annotate('text', label = '2022', x = -74.5, y = 43.5, size = 8, 
           colour = 'black' ) +
  coord_sf(xlim = c(-76,-66.0), ylim = c(35.5,44), datum = sf::st_crs(4326)) +
  xlab('Longitude') + 
  ylab('Latitude') +
  theme_bw() + 
  theme(legend.position = c(0.85, 0.2)) +
  theme(legend.background = element_rect(linetype="solid", 
                                         colour ="grey20")) +
  theme(legend.key.size = unit(0.5, 'cm')) + 
  theme(axis.text = element_text(size = 13), 
        axis.title = element_text(size = 15),
        axis.ticks.length = unit(-1.4, "mm")) 
# save
ggsave(path = here::here('figures'),'ilxsm_2022.png', 
       width = 10, height = 8, units = "in", dpi = 300) 

#2023
ggplot() +
 geom_sf(data = us.coast %>% st_as_sf(), color = 'gray20', fill = 'lightgrey') +
  geom_sf(data = ca.coast %>% st_as_sf(), color = 'gray20', fill = 'lightgrey') +
  geom_sf(data = ilxsm.stat.areas %>% st_as_sf() ,  
          fill = NA, color = 'gray20', lwd = 0.6) +
  geom_contour(data = bathy,
               aes(x=x,y=y,z=-1*z),
               breaks=c(0,50,100,200, Inf),
               linewidth=c(0.3),
               col = 'darkgrey') +
  geom_point(data = df_tally_stat %>% filter(year == 2023),
             aes(x = lon, y = lat, size = n), 
             color = 'black', bg = 'violetred1',
             pch = 21) +
  labs(size = 'No. of Squid') +
  geom_text()+
  annotate('text', label = '2023', x = -74.5, y = 43.5, size = 8, 
           colour = 'black' ) +
  coord_sf(xlim = c(-76,-66.0), ylim = c(35.5,44), datum = sf::st_crs(4326)) +
  xlab('Longitude') + 
  ylab('Latitude') +
  theme_bw() + 
  theme(legend.position = c(0.85, 0.2)) +
  theme(legend.background = element_rect(linetype="solid", 
                                         colour ="grey20")) +
  theme(legend.key.size = unit(0.5, 'cm')) + 
  theme(axis.text = element_text(size = 13), 
        axis.title = element_text(size = 15),
        axis.ticks.length = unit(-1.4, "mm")) 
# save
ggsave(path = here::here('figures'),'ilxsm_2023.png', 
       width = 10, height = 8, units = "in", dpi = 300) 
#2024
ggplot() +
 geom_sf(data = us.coast %>% st_as_sf(), color = 'gray20', fill = 'lightgrey') +
  geom_sf(data = ca.coast %>% st_as_sf(), color = 'gray20', fill = 'lightgrey') +
  geom_sf(data = ilxsm.stat.areas %>% st_as_sf() ,  
          fill = NA, color = 'gray20', lwd = 0.6) +
  geom_contour(data = bathy,
               aes(x=x,y=y,z=-1*z),
               breaks=c(0,50,100,200, Inf),
               linewidth=c(0.3),
               col = 'darkgrey') +
  geom_point(data = df_tally_stat %>% filter(year == 2024),
             aes(x = lon, y = lat, size = n), 
             color = 'black', bg = '#FFBE98',
             pch = 21) +
  labs(size = 'No. of Squid') +
  geom_text()+
  annotate('text', label = '2024', x = -74.5, y = 43.5, size = 8, 
           colour = 'black' ) +
  coord_sf(xlim = c(-76,-66.0), ylim = c(35.5,44), datum = sf::st_crs(4326)) +
  xlab('Longitude') + 
  ylab('Latitude') +
  theme_bw() + 
  theme(legend.position = c(0.85, 0.2)) +
  theme(legend.background = element_rect(linetype="solid", 
                                         colour ="grey20")) +
  theme(legend.key.size = unit(0.5, 'cm')) + 
  theme(axis.text = element_text(size = 13), 
        axis.title = element_text(size = 15),
        axis.ticks.length = unit(-1.4, "mm")) 
# save
ggsave(path = here::here('figures'),'ilxsm_2024.png', 
       width = 10, height = 8, units = "in", dpi = 300) 

```


### Length x weight across years

> Comparisons of mantle length and body weight across years

Bar Charts: 

Mean body weight (in grams) and mean mantle length (in millimeters) as a function 
of year. Error bars are 95% confidence limits. 

+ (2021): N = `r nrow(lw_paired %>% filter(year == 2021))`
+ (2022): N = `r nrow(lw_paired %>% filter(year == 2022))`
+ (2023): N = `r nrow(lw_paired %>% filter(year == 2023))`
+ (2024): N = `r nrow(lw_paired %>% filter(year == 2024))`


```{r, barchart}
wt_stats <- wt %>%
  group_by(year) %>%
  summarise(mean = mean(weight), 
            sd = sd(weight),
            min = min(weight), 
            max = max(weight))

ml_stats <- ml %>%
  group_by(year) %>%
  summarise(mean = mean(length), 
            sd = sd(length),
            min = min(length), 
            max = max(length))

wt_stats$param <- 'weight'
ml_stats$param <- 'mantle_length'


ilxsm_stats <- rbind(wt_stats, ml_stats)
ilxsm_stats$conf_interval <- (1.96*ilxsm_stats$sd)
# Labels outside bars: vjust = -0.5, Inside bars:  vjust = 1.6,
p1 = ggplot(data = wt_stats, aes(x = year, y = mean)) +
  geom_bar(stat ='identity', fill = c('gold1','slateblue3','violetred1', '#FFBE98'),
           col = 'black') +
  ylab('Mean weight (g)') +
  xlab('Year') +
  ylim(0,200) +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width=.2,
                position=position_dodge(.9)) + 
  ecodata::theme_ts()
p1 = p1 +  theme(text = element_text(size = 14), 
            axis.text = element_text(size = 13), 
            axis.title = element_text(size = 15),
            axis.ticks.length = unit(-1.4, "mm")) 


p2 = ggplot(data = ml_stats, aes(x = year, y = mean)) +
  geom_bar(stat ='identity', fill = c('gold1','slateblue3','violetred1', '#FFBE98'),
           col = 'black') +
  ylab('Mean mantle length (mm)') +
  xlab('Year') +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width=.2,
                position=position_dodge(.9)) + 
   ecodata::theme_ts()
p2 = p2 +  theme(text = element_text(size = 14), 
                 axis.text = element_text(size = 13), 
                 axis.title = element_text(size = 15),
                 axis.ticks.length = unit(-1.4, "mm")) 



p1 + p2
# save plot 
ggsave(path = here::here('figures'),'ilxsm_mean_length_weight_by_year.png', 
       width = 10, height = 8, units = "in", dpi = 300) 
```


2d Histograms:

Density heat maps of mantle length (mm) as a function of body weight (g) 
in year 1 (2021), year 2 (2022), year 3 (2023) and 4 (2024) of the 
Shortfin Squid Electronic Size Monitoring Pilot Project.

```{r, hist}
# 
# Consolidate dataset to only samples with paired weight/length values

# COlor palettes
pal <- wesanderson::wes_palette("Zissou1", 21, type = "continuous")
# 2d histogram with default option
# ggplot(lw_paired, aes(x=length, y=weight)) +
#   geom_bin2d() +
#   theme_bw()

# # Bin size control + color palette
# gd = ggplot(lw_paired, aes(x=length, y=weight)) +
#   geom_bin2d(bins = 70) +
#   scale_fill_gradientn(colours=pal) +
#   xlab('Mantle Length (mm)') +
#   ylab('Body Weight (g)') +
#   theme_bw()
# gd + theme(text = element_text(size = 14), 
#            axis.text = element_text(size = 13), 
#            axis.title = element_text(size = 15))



g3 = ggplot(lw_paired, 
            aes(x=length, y=weight)) +
  geom_hex() +
  scale_fill_gradientn(colours=pal) +
  xlab('Mantle Length (mm)') +
  ylab('Body Weight (g)') +
  labs(fill = 'Count') +
  ecodata::theme_facet() +
  facet_wrap(~year)
g3 + theme(text = element_text(size = 14), 
           axis.text = element_text(size = 13), 
           axis.title = element_text(size = 15),
           legend.position = c(0.92, 0.23), 
           legend.background = element_rect(fill = "white", color = "black"), 
           legend.title = element_text(size = 7),
           legend.text = element_text(size = 7)) 


ggsave(path = here::here('figures'),'ilxsm_2dhist_by_year.png', 
       width = 10, height = 8, units = "in", dpi = 300) 

```



### 2024 ILXSM data

Weekly distributions of northern shortfin squid (Illex illecebrosus)
body weight (in grams) and mantle length (in millimeters) samples for 2024. 

The figures below represent the size of squid over time, where squid weight 
(or length) increases from left to right, with specific weight (or length) 
values labeled along the horizontal line (axis) under the ridge (peach area). 
The height of the ridge relates to the number of squid at the corresponding 
weight on the horizontal axis. 

+ For instance, the greater the height at a given weight, the more squid are 
found at that weight.
+ The wider the base of the ridge, the wider range of weights of the squid 
sampled, thus the more variable the sizes collected that week were.

The ridgeplots with color gradients represent the empirical cumulative density 
function for the distribution. Here, the probabilities are mapped onto color.

```{r, ridgeplots}
# Lengths
ggplot(ml %>% filter(year == 2024), aes(x = length, y = factor(week))) +
    ggridges::geom_density_ridges(alpha = 0.7, rel_min_height = 0.001, fill='#f6a192') + 
  labs(title = '2024 Illex Lengths',
       x = 'Lengths (mm)', y = 'Week of Year') +
  ecodata::theme_ts()

ggplot(ml %>% filter(year == 2024), aes(x = length, y = factor(week),
                                           fill = 0.5 - abs(0.5 - stat(ecdf))))  +
  ggridges::stat_density_ridges(calc_ecdf = TRUE, rel_min_height = 0.0001,
                      geom = "density_ridges_gradient") +
  labs(title = '2024 Illex Lengths',
       x = 'Weight (gm)', y = 'Week of Year') +
  scale_fill_viridis_c(name = 'Tail probability', direction = -1) +
  ecodata::theme_ts()

# Weight
ggplot(wt %>% filter(year == 2024), aes(x = weight, y = factor(week))) +
   ggridges::geom_density_ridges(alpha = 0.7, rel_min_height = 0.001, 
                                           fill='#f6a192') + 
  labs(title = '2024 Illex Weights',
       x = 'Weight (gm)', y = 'Week of Year') +
  ecodata::theme_ts()


ggplot(wt %>% filter(year == 2024), aes(x = weight, y = factor(week),
                                           fill = 0.5 - abs(0.5 - stat(ecdf))))  +
  ggridges::stat_density_ridges(calc_ecdf = TRUE, rel_min_height = 0.0001,
                      geom = "density_ridges_gradient") +
  labs(title = '2024 Illex Weights',
       x = 'Weight (gm)', y = 'Week of Year') +
  scale_fill_viridis_c(name = 'Tail probability', direction = -1) +
  ecodata::theme_ts()
# # save
# ggsave(path = here::here('figures'),'ilxsm_mean_length_weight_by_year.png', 
#        width = 10, height = 8, units = "in", dpi = 300) 
```


