---
title: "Ind_Ves_Poster_Plotting"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Description
This is ... TBA


# Setting global options

```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=6, fig.path='Figs/',
                      echo=TRUE, warning=FALSE, message=FALSE)
```

# Loading packages
Loading the many packages that are used somewhere in this script. This script has evolved to do many things and many of these are only need in one or two places.

```{r Loading packages}
#loading needed packages
#Not all of these are needed right away
library(tidyverse)
library(lubridate) #dates

```

# Setting up DB connection
Setting up connections to SOLE and NOVA using ROracle. Don't need to run, but could be set up. Needs an additional file and some other software installation.

```{r Setting up DB connection}
#File path may need to change
source('C:/Users/andrew.jones/Desktop/dbconnection_v3.R')

```

# Pulling the data from the new view

```{r}
library(dbplyr)
dbGetQuery(con,"SET ROLE ALL")

trip <- dplyr::tbl(con, dbplyr::in_schema("FVTR", "COMBINED_VERS_VIEW"))
trip_tot  <- trip %>% group_by(TRIP_ID) %>% summarise(SUM=sum(HAIL_AMOUNT,na.rm=TRUE)) %>% collect()

sql_pull <- "SELECT * from fvtr.COMBINED_VERS_VIEW WHERE SPECIES_ITIS in (82372)"

sql_pull_db <- dbGetQuery(con,sql_pull)

conversion_factors_cfdbs <- dbGetQuery(con,"select * from CFDBS.SPECIES_ITIS_NE")

species_itis_common <- conversion_factors_cfdbs %>% group_by(SPECIES_ITIS,COMMON_NAME) %>% tally() %>% as.data.frame()

```

# Cams data 

Pulling and making a set of targeted trips (> 0.39 longfin catch)

```{r}
library(dbplyr)
cams <- dplyr::tbl(con.nova, dbplyr::in_schema("CAMS_GARFO", "CAMS_LANDINGS"))
cams_lf_tot  <- cams %>% filter(ITIS_TSN == 82372) %>% collect()

cams_trip_tot  <- cams %>% group_by(DOCID) %>% summarise(SUM=sum(LIVLB,na.rm=TRUE)) %>% collect()

cams_lf_tot_target <- cams_lf_tot  %>% 
                          left_join(.,cams_trip_tot) %>% mutate(PROP_LONGFIN=LIVLB/SUM) %>%
                          filter(PROP_LONGFIN > 0.399)

```

# Looking at longfin catch

```{r}
library(gt)

trips_by_month <- sql_pull_db %>% 
  group_by(SAIL_YEAR,TRIP_ID,SAIL_MONTH,VESSEL_NAME) %>% 
  distinct(TRIP_ID) %>% as.data.frame() %>% 
  group_by(SAIL_YEAR,SAIL_MONTH) %>%
  tally() %>% 
  arrange(SAIL_MONTH) %>%
  mutate(SAIL_MONTH = month.abb[SAIL_MONTH]) %>%
  pivot_wider(values_from = n,names_from = SAIL_YEAR)

vessels_by_month <- sql_pull_db %>% 
  group_by(SAIL_YEAR,SAIL_MONTH,VESSEL_NAME) %>% 
  distinct(VESSEL_NAME) %>% as.data.frame() %>% 
  group_by(SAIL_YEAR,SAIL_MONTH) %>%
  tally() %>% 
  arrange(SAIL_MONTH) %>%
  mutate(SAIL_MONTH = month.abb[SAIL_MONTH]) %>%
  pivot_wider(values_from = n,names_from = SAIL_YEAR)

weight_by_month <- sql_pull_db %>% 
  group_by(SAIL_YEAR,SAIL_MONTH) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  arrange(SAIL_MONTH) %>%
  mutate(SAIL_MONTH = month.abb[SAIL_MONTH]) %>%
  pivot_wider(values_from = SUM_WT,names_from = SAIL_YEAR)

weight_by_area <- sql_pull_db %>% 
  group_by(SAIL_YEAR,FA_AREA_CODE) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  pivot_wider(values_from = SUM_WT,names_from = SAIL_YEAR)
  
weight_by_port <- sql_pull_db %>% 
  group_by(SAIL_YEAR,END_PORT) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  pivot_wider(values_from = SUM_WT,names_from = SAIL_YEAR)

weight_by_port %>% gt()

weight_by_area %>% gt() 

weight_by_month %>% gt()

vessels_by_month %>% gt()

trips_by_month %>% gt()

```

# Putting things in a excel workbook

```{r}
require(openxlsx)

list_of_datasets <- list("Trips_by_month" = trips_by_month, 
                         "Vessels_by_month" = vessels_by_month,
                         "Weight_by_month" = weight_by_month, 
                         "Weight_by_port" = weight_by_port,
                         "Weight_by_area" = weight_by_area
                         )
write.xlsx(list_of_datasets, file = "Longfin_Study_Fleet.xlsx")


```

# Looking at longfin catch

```{r}
library(gt)

sql_pull_db_target <- sql_pull_db %>% 
                          left_join(.,trip_tot) %>% mutate(PROP_LONGFIN=HAIL_AMOUNT/SUM) %>%
                          filter(PROP_LONGFIN > 0.399)

trips_by_month_targ <- sql_pull_db_target %>% 
  group_by(SAIL_YEAR,TRIP_ID,SAIL_MONTH,VESSEL_NAME) %>% 
  distinct(TRIP_ID) %>% as.data.frame() %>% 
  group_by(SAIL_YEAR,SAIL_MONTH) %>%
  tally() %>% 
  arrange(SAIL_MONTH) %>%
  mutate(SAIL_MONTH = month.abb[SAIL_MONTH]) %>%
  pivot_wider(values_from = n,names_from = SAIL_YEAR) %>%
  select(SAIL_MONTH,sort(names(.)))

vessels_by_month_targ <- sql_pull_db_target %>% 
  group_by(SAIL_YEAR,SAIL_MONTH,VESSEL_NAME) %>% 
  distinct(VESSEL_NAME) %>% as.data.frame() %>% 
  group_by(SAIL_YEAR,SAIL_MONTH) %>%
  tally() %>% 
  arrange(SAIL_MONTH) %>%
  mutate(SAIL_MONTH = month.abb[SAIL_MONTH]) %>%
  pivot_wider(values_from = n,names_from = SAIL_YEAR) %>%
  select(SAIL_MONTH,sort(names(.)))

weight_by_month_targ <- sql_pull_db_target %>% 
  group_by(SAIL_YEAR,SAIL_MONTH) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  arrange(SAIL_MONTH) %>%
  mutate(SAIL_MONTH = month.abb[SAIL_MONTH]) %>%
  pivot_wider(values_from = SUM_WT,names_from = SAIL_YEAR) %>%
  select(SAIL_MONTH,sort(names(.)))

weight_by_area_targ <- sql_pull_db_target %>% 
  group_by(SAIL_YEAR,FA_AREA_CODE) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  pivot_wider(values_from = SUM_WT,names_from = SAIL_YEAR) %>%
  select(FA_AREA_CODE,sort(names(.)))
  
weight_by_port_targ <- sql_pull_db_target %>% 
  group_by(SAIL_YEAR,END_PORT) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  pivot_wider(values_from = SUM_WT,names_from = SAIL_YEAR) %>%
  select(END_PORT,sort(names(.)))

weight_by_port_targ %>% gt()

weight_by_area_targ %>% gt() 

weight_by_month_targ %>% gt()

vessels_by_month_targ %>% gt()

trips_by_month_targ %>% gt()

```

# Putting things in a excel workbook

```{r}
require(openxlsx)

list_of_datasets <- list("Trips_by_month_targ" = trips_by_month_targ, 
                         "Vessels_by_month_targ" = vessels_by_month_targ,
                         "Weight_by_month_targ" = weight_by_month_targ, 
                         "Weight_by_port_targ" = weight_by_port_targ,
                         "Weight_by_area_targ" = weight_by_area_targ
                         )
write.xlsx(list_of_datasets, file = "Longfin_Study_Fleet_Targeted.xlsx")


```

# Study Fleet targeted trips as proportion of total (CAMS)

For the 'targeted' subset of both

```{r}

cams_sums <- cams_lf_tot_target %>% group_by(MONTH,YEAR) %>% summarise(SUM_CAMS=sum(LIVLB,na.rm = TRUE))

sf_sums <- sql_pull_db_target %>% mutate(MONTH = SAIL_MONTH, YEAR = SAIL_YEAR) %>% 
  group_by(MONTH,YEAR) %>% summarise(SUM_SF=sum(HAIL_AMOUNT,na.rm = TRUE))

prop_sf_target <- left_join(cams_sums,sf_sums) %>% filter(YEAR > 2010) %>%
  mutate(PROP_SF = SUM_SF/SUM_CAMS) %>%
  as.data.frame() %>%
  dplyr::select(-SUM_CAMS,-SUM_SF) %>%
  pivot_wider(values_from = PROP_SF,names_from = YEAR)

prop_sf_target %>% gt()
  
```

# Putting things in a excel workbook

```{r}
require(openxlsx)

list_of_datasets <- list("Prop_sf_target" = prop_sf_target
                         )
write.xlsx(list_of_datasets, file = "Longfin_Study_Fleet_CAMS_Targeted.xlsx")

```


# Looking at longfin catch

```{r}
library(gt)

sql_pull_db_target <- sql_pull_db %>% 
                          left_join(.,trip_tot) %>% mutate(PROP_LONGFIN=HAIL_AMOUNT/SUM) %>%
                          filter(PROP_LONGFIN > 0.399)
  
weight_by_vessel_targ <- sql_pull_db_target %>% 
  group_by(SAIL_YEAR,VESSEL_NAME) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  pivot_wider(values_from = SUM_WT,names_from = SAIL_YEAR) %>%
  arrange(-`2022`)

weight_by_vessel_targ_2022 <- sql_pull_db_target %>% filter(SAIL_YEAR == 2022) %>%
  group_by(SAIL_MONTH,VESSEL_NAME) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  pivot_wider(values_from = SUM_WT,names_from = SAIL_MONTH)

weight_by_vessel_targ_2021 <- sql_pull_db_target %>% filter(SAIL_YEAR == 2021) %>%
  group_by(SAIL_MONTH,VESSEL_NAME) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  pivot_wider(values_from = SUM_WT,names_from = SAIL_MONTH)

weight_by_vessel_targ_2020 <- sql_pull_db_target %>% filter(SAIL_YEAR == 2020) %>%
  group_by(SAIL_MONTH,VESSEL_NAME) %>% 
  summarise(SUM_WT = sum(HAIL_AMOUNT,na.rm=TRUE)) %>% 
  as.data.frame() %>% 
  pivot_wider(values_from = SUM_WT,names_from = SAIL_MONTH)

weight_by_vessel_targ %>% gt()

weight_by_vessel_targ_2022 %>% gt() 

weight_by_vessel_targ_2021 %>% gt()

weight_by_vessel_targ_2020 %>% gt()

```

# Putting things in a excel workbook

```{r}
require(openxlsx)

list_of_datasets <- list("Weight_by_vessel_targ" = weight_by_vessel_targ, 
                         "Weight_by_vessel_targ_2022" = weight_by_vessel_targ_2022,
                         "Weight_by_vessel_targ_2021" = weight_by_vessel_targ_2021, 
                         "Weight_by_vessel_targ_2020" = weight_by_vessel_targ_2020
                         )
write.xlsx(list_of_datasets, file = "Longfin_Study_Fleet_Targeted_Vessels.xlsx")


```

