---
title: "merge_weights"
author: "Sarah Salois"
output:
 html_document:
    code_fold: hide
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages & Data wrangling

Below, I pull in data from the Lisa Hendrickson via the Research Track Working 
Group and Thomas Swaider via the ILXSM project. 

```{r, warning=FALSE, message=FALSE}
library(lubridate)
library(dplyr)
library(ggplot2)
library(patchwork)
# Data files
# This is the data Lisa Hendrickson provided to the working group
bw <- read.csv('illex_bodywts.csv')
# This is ILXSM data I wrangled and saved in file called 'plot_lw_figures.R'
df_full <- read.csv('ilxsm_weights_lengths.csv')
# dat is a subset of the ilxsm data where I select just paired data
dat <- df_full[!is.na(c(df_full$lengths & df_full$weights )), ]
# Fix date and add a few new time-related variables
bw$DATE <- as.Date(bw$DATE)
bw <- bw %>%
  mutate(year = year(DATE),
         month = month(DATE),
         week = week(DATE), 
         day = day(DATE)) %>%
  as.data.frame()
# Isolate FV/DARANA to examine data
darana <- bw %>% filter(HULLNUM == 536245)
# DARANA vessel id = JAZL 
# wrangle ILXSM data to merge with Lisa's data for DARANA
darana2 = dat %>% filter(vessel_id == 'JAZL') %>% 
  rename(DATE = LAND_DATE, 
         BODYWT = weights) %>% 
  mutate(month = month(DATE),
         day = day(DATE))
darana2$HULLNUM <- 536245
darana2 <- darana2 %>% select('HULLNUM', "DATE", 'BODYWT',
                              'year','month', 'week', 'day')

darana9922 <- rbind(darana, darana2)

# Let's add all ILXSM data together 
ilxsmdf <- df_full %>%
  select('year', 'week', 'LAND_DATE', 'weights', 
         'VESSEL_NAME.x','vessel_id', 'hold_type') %>% 
  rename(DATE = LAND_DATE, 
         BODYWT = weights) %>% 
  mutate(month = month(DATE),
         day = day(DATE)) 

# Find/extract/pair the hullnum to vessel name from CFDBS_vessels_1997-2019 file

v.ids <- read.csv('CFDBS_vessels_1997-2019.csv')

ilxsmdf$HULLNUM <- NA
uvn <- sort(unique(ilxsmdf$VESSEL_NAME.x))

for (i in 1:length(uvn)){
  a <- subset(v.ids, VESSNAME == uvn[i])
  locs <- which(ilxsmdf$VESSEL_NAME %in% a$VESSNAME)
  ilxsmdf[locs,10] <- a[1,3]
}


# Get this ready to merge
ilxsmdf2 <- ilxsmdf %>% select('HULLNUM', "DATE", 'BODYWT',
                              'year','month', 'week', 'day')


# merge ilxsm data to Lisa's
bwts <- rbind(bw, ilxsmdf2)


## Now add permits & vessel name just to be thorough for comparing data later 
bwts$permit <- NA
bwts$vessel_name <- NA

for (i in 1:length(uvn)){
  a <- subset(v.ids, VESSNAME == uvn[i])
  locs <- which(bwts$HULLNUM %in% a$HULLNUM)
  bwts[locs,8] <- a[1,2]
  bwts[locs,9] <- a[1,4]
  
}


```

## Plotting 

Looking at patterns in Illex catch weight for the vessel DARANA

```{r, warning=FALSE, message=FALSE}
# Just DARANA
ggplot(darana9922, aes(x = factor(year), y = BODYWT)) + 
    labs(x = 'Year',
         y = 'Weight (g)',
         title = 'Darana') +
    theme_classic() +
    guides(fill=guide_legend(title=NULL))+
    geom_boxplot()
# ggsave(path = here::here('results'),'Darana_weights.jpg', 
#        width = 8, height = 3.75, units = "in", dpi = 300)

```


Merged the data made available to the Illex RT working group by Lisa 
Hendrickson and the data from the ILXSM project to view patterns of Illex 
weight over time 

```{r, warning=FALSE, message=FALSE}
# All weights (Lisa + ILXSM)
ggplot(bwts, aes(x = factor(year), y = BODYWT)) + 
  labs(x = 'Year',
       y = 'Weight (g)') +
  theme_classic() +
  guides(fill=guide_legend(title=NULL))+
  geom_boxplot()
# ggsave(path = here::here('results'),'all_weights.jpg', 
#        width = 8, height = 3.75, units = "in", dpi = 300)

```



```{r, warning=FALSE, message=FALSE}
# All weights (Lisa + ILXSM) ordered by median
p1 = ggplot(bwts, 
       aes(x = reorder(factor(year),BODYWT, median, na.rm = TRUE), y = BODYWT, 
           fill = factor(year))) + 
  labs(x = 'Year',
       y = 'Weight (g)', 
       title = 'Illex body weights (WG + ILXSM)',
       subtitle = 'Ordered by median') +
  theme_classic() +
  guides(fill = FALSE)+
  geom_boxplot()
# ggsave(path = here::here('results'),'all_weights_median.jpg', 
#        width = 8, height = 3.75, units = "in", dpi = 300)
p2 = ggplot(bwts, 
       aes(x = reorder(factor(year),BODYWT, mean, na.rm = TRUE), y = BODYWT, 
           fill = factor(year))) + 
  labs(x = 'Year',
       y = 'Weight (g)', 
       title = 'Illex body weights (WG + ILXSM)',
       subtitle = 'Ordered by mean') +
  theme_classic() +
  guides(fill = FALSE)+
  geom_boxplot()
# ggsave(path = here::here('results'),'all_weights_mean.jpg', 
#        width = 8, height = 3.75, units = "in", dpi = 300)



#p1/p2

```






```{r, warning=FALSE, message=FALSE}
p1
```






```{r, warning=FALSE, message=FALSE}
p2
```

## Time series

```{r, warning=FALSE, message=FALSE}


bw_tally <- bwts %>% 
  group_by(year) %>%
  summarise(mean.wt = mean(na.omit(BODYWT)), 
            sd.wt = sd(na.omit(BODYWT)), 
            max.wt = max(na.omit(BODYWT)),
            min.wt = min(na.omit(BODYWT)),
            n = length(na.omit(BODYWT)))
yrs = unique(bw_tally$year)

```


Visualizing the time series and applying a trend analysis. Since this is a 
relatively short time series (23 years), the function from geom_gls() from 
ecodata will not work. This function fits four trend models to each time series,
uses AICc to select the best model fit, and then implements a likelihood-ratio 
test to determine if a trend is present. If a significant trend is 
present (P < 0.05), then the trend line is plotted with the series.
By default, a purple line color is assigned to negative trends and 
orange to positive trends. 
More details on this function [here](https://noaa-edab.github.io/tech-doc/trend-analysis.html) 

```{r, warning=FALSE, message=FALSE}

ggplot(bw_tally, aes(x = year, y = mean.wt)) +
  geom_line() +
  #geom_smooth() +
  ecodata::geom_gls() +
  # xlim(1997,2022) +
  # scale_x_continuous(breaks = function(range) seq(yrs[1], yrs[23], by = 1))+
  theme_bw()
```

Adding in a LOESS (Locally Weighted Scatterplot Smoothing) trend line. LOESS
is non-parametric regression technique

```{r, warning=FALSE, message=FALSE}
ggplot(bw_tally, aes(x=year, y= mean.wt)) +
  geom_point() +
  geom_smooth() +
  theme_bw()
```








