---
title: "maturity_data_analysis"
author: "Sarah Salois"
output: 
 html_document:
    code_fold: hide
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE, warning=FALSE, message = FALSE}
library(plyr)
library(dplyr)
library(sp)
library(ggplot2)
library(rgdal)
library(RColorBrewer)
library(mapdata)
library(marmap)
library(raster)
library(sf)
library(tidyverse)
library(fields)
library(readxl)
library(interp)
library(leaflet)
library(wesanderson)
library(scales)
library(ggnewscale)
library(ggridges)
library(ggpubr)
library(contourPlot)
library(TAM)
library(Hmisc)

```


## Data Wrangling 
The code below reads in the data, calculates maturity for females by 
computing the nidamental gland index (the length of the nidamental gland
divided by the dorsal mantle length) and comparing it to the following table
from Durward et al. 1979: 

**Maturity index** 
Maturation stages for female shortfin squid (m): 
Stage I: m ≤ 0.09
Stage II: 0.05 < m ≤ 0.125
Stage III: 0.125 < m ≤ 0.20
Stage IV:  0.20 < m ≤ 0.35
Stage V: 0.35 < m

*Durward, R.D., Amaratunga, T. and O’Dor, R.K., 1979. Maturation index and fecundity for female squid, Illex illecebrosus (LeSueur, 1821). ICNAF Res. Bull, 14, pp.67-72.*


```{r, message=FALSE, warning= FALSE}
# read in maturity data sets
prevail <- read.csv(here::here('data/maturity_data_prevail.csv'))
seafarer <- read.csv(here::here('data/maturity_data_seafarer.csv'))
# Calulate Nidamental Gland Index 
prevail$ngi <- (prevail$ngl)/(prevail$ml) # NGI == nidamental gland index
prevail = prevail %>% 
  mutate(
    mat_stage_m = mat_stage,
    mat_stage_f = case_when(
      ngi < 0.09 ~ 1, 
      ngi > 0.05 & ngi < 0.125 ~ 2, 
      ngi > 0.125 & ngi < 0.20 ~ 3, 
      ngi > 0.20 & ngi < 0.35 ~ 4, 
      ngi > 0.35  ~ 5
    ))

seafarer$ngi<- (seafarer$ngl)/(seafarer$ml)
seafarer = seafarer %>% 
  mutate(
    mat_stage_m = mat_stage,
    mat_stage_f = case_when(
      ngi < 0.09 ~ 1, 
      ngi > 0.05 & ngi < 0.125 ~ 2, 
      ngi > 0.125 & ngi < 0.20 ~ 3, 
      ngi > 0.20 & ngi < 0.35 ~ 4, 
      ngi > 0.35  ~ 5
    ))  


# merge the data sets 
df <- rbind(prevail, seafarer)
df$date <-lubridate::mdy(df$date)
df <- df %>%
  mutate(year = lubridate::year(date),
         month = lubridate::month(date),
         week = lubridate::week(date), 
         day = lubridate::day(date))
# color palette
wespal <- wes_palette("Zissou1")
wespal2 <- wes_palette("Zissou1", 10, type = "continuous")

```

## Female  

### Mantle length as a function of nidamental gland length 

```{r}
g <- ggplot(df, aes(ml, ngl)) +           
  geom_point() + 
  xlab('Mantle length (mm)') + 
  ylab('Nidamental gland length (mm)') +
  ecodata::theme_ts() + 
  facet_wrap(~vessel_name)

g + stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth") + 
   stat_cor(label.y = 70)+ #this means at 35th unit in the y axis, the r squared and p value will be shown
        stat_regline_equation(label.y = 76) #this means at 30th unit regresion line equation will be shown

ggscatter(
  df, x = "ml", y = "ngl",
  add = "reg.line"
) +
  facet_wrap(~vessel_name) +
  stat_cor(label.y = 155) +
  stat_regline_equation(label.y = 165)

ggscatter(
  df, x = "ml", y = "ngl",
  add = "reg.line"
) +
  stat_cor(label.y = 155) +
  stat_regline_equation(label.y = 165)



```



```{r, warning=FALSE}
g <- ggplot(df %>% filter(vessel_name == 'Seafarer'), aes(ml, ngl)) +
  geom_point() + 
  xlab('Mantle length (mm)') + 
  ylab('Nidamental gland length (mm)') +
  ecodata::theme_ts() 
g + stat_smooth(method = "lm",
                formula = y ~ x,
                geom = "smooth") + 
  stat_cor(label.y = 70)+ 
  stat_regline_equation(label.y = 76)
```



```{r}
hist(prevail$mat_stage_f, xlab = 'Maturation Stage (m)',
     main = '', xlim = c(1,5))
hist(seafarer$mat_stage_f, xlab = 'Maturation Stage (m)',
     main = '', xlim = c(1,5))
p <-ggplot(df, aes(x = mat_stage_f)) + 
   geom_histogram(color="black", fill="grey45",  binwidth = 0.9) + 
   xlab('Female Maturity Stage (m)') +
   facet_wrap(~vessel_name) + 
   theme_classic2()
p
```



```{r}
p <-ggplot(df, aes(x = mat_stage_f, fill = as.factor(vessel_name))) + 
   geom_bar(position = position_dodge(), alpha = 0.4, color="black", 
                  binwidth = 0.5) + 
   xlab('Female Maturity Stage (m)') +
   labs(fill = 'Vessel') +
   theme_bw()
p
```




## Male

### Maturity index 
Maturation stages: 
Stage 1: immature, no spermatophores
Stage 2: maturing I, no spermatophores 
Stage 3: maturing II, no to several spermatophores 
Stage 4: mature, spermatophores present

```{r, warning=FALSE, message=FALSE}
ggplot(df, aes(mat_stage)) +
    geom_bar(color="black", fill="grey35") +
   xlab('Male Maturity stage') +
    facet_wrap(~vessel_name) + 
  theme_bw()
```


```{r}
p <-ggplot(df, aes(x = mat_stage, fill = as.factor(vessel_name))) + 
   geom_bar(position = "identity", alpha = 0.4, color="black") + 
   xlab('Male Maturity Stage (m)') +
   labs(fill = 'Vessel') +
   theme_bw()
p
```




```{r}
ggplot(df %>% filter(vessel_name == 'Seafarer'), aes(mat_stage)) +
    geom_bar(color="black", fill="grey35") +
   xlab('Male Maturity stage') +
   
  theme_bw()
```

## Length-weight relationships 

### Ridge plots 

Looking at distribution of weights and lengths by sex for each sample. The sample from Prevail was from October 2022 and the sample from Seafarer was from February 2023.  

```{r, warning=FALSE, message=FALSE}
ggplot(df,
       aes(x = wt, y = factor(sex), 
                          fill = stat(quantile))) +
  stat_density_ridges(quantile_lines = FALSE,
                      calc_ecdf = TRUE, rel_min_height = 0.0001,
                      geom = "density_ridges_gradient") +
  labs(x = 'Weights (g)', y = 'Sex') +
  scale_fill_brewer(name = 'Quartiles', palette = 'Greys') +
  ecodata::theme_ts() + 
  facet_wrap(~vessel_name)
```


```{r, warning=FALSE, message=FALSE}
ggplot(df %>% filter(sex %in% c('M','F')),
       aes(x = wt, y = factor(sex), 
                          fill = vessel_name)) +
  geom_density_ridges(alpha = 0.7) +
  labs(fill = 'Vessel Name') +
  # stat_density_ridges(quantile_lines = FALSE,
  #                     calc_ecdf = TRUE, rel_min_height = 0.0001,
  #                     geom = "density_ridges_gradient") +
  labs(x = 'Weights (g)', y = 'Sex') +
 # scale_fill_brewer(name = 'Quartiles', palette = 'Greys') +
  ecodata::theme_ts()
```








```{r, warning=FALSE, message=FALSE}
ggplot(df,
       aes(x = ml, y = factor(sex), 
                          fill = stat(quantile))) +
  stat_density_ridges(quantile_lines = FALSE,
                      calc_ecdf = TRUE, rel_min_height = 0.0001,
                      geom = "density_ridges_gradient") +
  labs(x = 'Mantle length (mm)', y = 'Sex') +
  scale_fill_brewer(name = 'Quartiles', palette = 'Greys') +
  ecodata::theme_ts() + 
  facet_wrap(~vessel_name)
```



```{r, warning=FALSE, message=FALSE}
ggplot(df %>% filter(sex %in% c('M','F')),
       aes(x = ml, y = factor(sex), 
                          fill = vessel_name)) +
  geom_density_ridges(alpha = 0.7) +
  labs(fill = 'Vessel Name') +
  labs(x = 'Mantle length (mm)', y = 'Sex') +
  ecodata::theme_ts()
```





### Males & females combined

Length as a function of weight for both sexes and samples combined. 

```{r}
g <- ggplot(df, aes(ml, wt)) +           
  geom_point() + 
  xlab('Mantle length (mm)') + 
  ylab('Body weight (g)') +
  ecodata::theme_ts()

g + stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth")
```

Length as a function of weight for both sexes seperated by sample. 

```{r}
g <- ggplot(df, aes(ml, wt)) +           
  geom_point() + 
  xlab('Mantle length (mm)') + 
  ylab('Body weight (g)') +
  ecodata::theme_ts() + 
  facet_wrap(~vessel_name)

g + stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth")
```



### Males vs females 

Length as a function of weight for males and females seperately. Here, I 
indicate if the sex was indeterminate for that sample.  


```{r, warning=FALSE}

# mod = lm(ml ~ wt, data = df)
# summary(mod)$coefficients

g <- ggplot(df, aes(ml, wt)) +           
  geom_point() + 
  xlab('Mantle length (mm)') + 
  ylab('Body weight (g)') +
  ecodata::theme_ts() + 
  facet_wrap(~sex)

g + stat_smooth(method = "lm",
              formula = y ~ x,
              geom = "smooth")


ggscatter(
  df, x = "ml", y = "wt",
  color = "sex", palette = "jco",
  add = "reg.line"
) +
  facet_wrap(~sex) +
  stat_cor(label.y = 155) +
  stat_regline_equation(label.y = 165)

```


## Age at weight estimates 

Code below computes age estimate for each weight
Parameters of weight at age estimation per Hendrickson and Hart 2006 
for males and females combined. The formula for Weight as a function of Age 
is: weight = alpha * age^beta, therefore age estimate is the 
inverse: (weight/alpha)^(1/beta)

### Frequency tables

Generate weight/length frequencies 

```{r}
tabp = table(prevail$wt) 
tabs = table(seafarer$wt) 
tab.s = seafarer %>% group_by(wt) %>% tally() 
```

```{r}
library(patchwork)
# estimate age in days
alpha<-1.12e-6
beta<-3.60
# df$age.est<-(df$wt/alpha)^(1/beta)
tab.p = table(subset(df, vessel_name == 'Prevail', 
                                    select = wt))
tab.s = table(subset(df, vessel_name == 'Seafarer', 
                                    select = wt))
barplot(tab.p, main=paste('Weight frequency for Seafarer sample collected in week 43'),
        xlab = 'Weight (g)', ylab = 'Frequency', col='deeppink')
barplot(tab.s, main=paste('Weight frequency for Seafarer sample collected in week 7'),
        xlab = 'Weight (g)', ylab = 'Frequency', col='deeppink')
tab.age.p = table(round(subset(df, vessel_name == 'Seafarer', select = age.est)))
tab.age.s = table(round(subset(df, vessel_name == 'Seafarer', select = age.est)))
barplot(tab.age.p, main=paste('Age frequency for Prevail sample collected in week 43'),
        xlab = 'Age in days', ylab = 'Frequency', col='blue')
barplot(tab.age.s, main=paste('Age frequency for Seafarer sample collected in week 7'),
        xlab = 'Age in days', ylab = 'Frequency', col='blue')
# Analysis of putative  Birth weeks
# Compute birth week as function of age at capture
# df$birth.week  <- round(df$week-df$age.est/7)  
b.week.table.p <- table(round(subset(df, vessel_name == 'Prevail', 
                                    select = birth.week)))
b.week.table.s <- table(round(subset(df, vessel_name == 'Seafarer', 
                                    select = birth.week)))
barplot(b.week.table.p, 
        main = paste('Birthweek frequency for Prevail sample collected in week 43'),
        xlab='Birth Week', ylab='Frequency', col='red')
barplot(b.week.table.s, 
        main = paste('Birthweek frequency for Seafarer sample collected in week 7'),
        xlab='Birth Week', ylab='Frequency', col='red')



```



